


\section{Introduction and Motivation}
Capital Asset Pricing Model (CAPM) (\citeA{Sharpe1964}, \citeA{Lintner1965}, and \citeA{Black1972}) introduces a risk pricing paradigm.
By incorporating factors, the model divides asset's risk into two parts: systematic risk and asset specified idiosyncratic risk.
In general, the market factor captures the systematic risk, and different risk factors price the idiosyncratic risk.
Researches (see \citeA{Fama1992}, \citeA{Carhart1997}, \citeA{Kelly2019}) have shown that, adding different risk factors into the CAPM model can enhance the ability of pricing risk.
Because of this, identifying risk factors has becomes an important topic in finance.
%Some famous examples of multi-factor CAPM include the Fama-French (FF) three-factor model \cite{Fama1992}, and the Momentum model \cite{Carhart1997}.
% Researchers after them are trying to find new risk factors to include in the multi-factor CAPM model.
Numerous of researchers have contributed to this field, and the direct result is a explosive growth of factors.
 \citeA{Harvey2019} have collected over 500 factors from papers published in the top financial and economic journals, and they find the growth of new factors has speed up since 2008. 
%In his 2011 presidential address, \citeauthor{Cochrane2011} coined the term "factor zoo" to describe the situation factor modelling is facing: researchers and practitioners have too many options when pricing the risk

%In those famous multi-factor model like FF three-factor model \cite{Fama1992}, the loadings of risk factors pass the significant test comfortably, but this is not always the case. 
But we should notice that not all factors can pass the significance test comfortably every time like the market factor.
Therefore, \citeA{Pesaran2019 introduced} a new criteria for assessing the significance of each factor, which they call it factor strength.
In general, if a factor can generate loadings significantly different from zero for all assets, then we call such a factor strong factor.
And the less significant loading a factor can generate, the weaker the strength it has.

In his 2011 president address \citeauthor{Cochrane2011} gave emphasis to the importance of finding factors which can provide independent information about average return and risk.
With regard to this, a number of scholars applied various methods to find such factors. 
%Since in their 2015 research \citeA{Harvey2015} argues that the current threshold for a test of parameter significant is too low for newly proposed factors, 
For instance, \citeA{Harvey2017} provided a bootstrap method to adjust the threshold of factor loading's significant test, trying to exclude some falsely significant factor caused by multiple-test problem.
Some other scholars are using machine learning methods to reduce the potential candidates. 
One stream of them have used a shrinkage and subset selection method called Lasso \cite{Tibshirani1996} and it's variations to find suitable factors.
One example of such application is made by \citeA{Rapach2013}.
They applied the Lasso regression, trying to find some characteristics from a large group to predict the global stock market's return.

But an additional challenge is that factors, especially in the high-dimension, are commonly correlated.
%\citeA{Cochrane2005} argues that the correlation between factors will reduce the ability of using risk premium to infer factors.
\citeA{Kozak2020} point out that when facing a group of correlated factors, Lasso will only pick several highly correlated factors seemly randomly, and then ignore the other and shrink them to zero. 
In other words, Lasso fails to handle the issue of correlated factors appropriately.


%\citeA{Kan1999} found that the test-statistic of FM two-stage regression  \cite{Fama1973} will inflate when incorporating factors which are independent with the cross-section return.
%Provides spurious factors with the chance  to pass the significant test.

%\citeA{Hou2018} found that they can not replicate the result of over 60\% selected factor papers. 

%These discoveries cast doubt on the risk pricing ability of some factors, indicates that some factors may fail to pass the significant test in certain scenarios.

Therefore, the main empirical question in this project is: how to select useful factors from a large group of possibly highly correlated candidates.
We address this question from two different prospects.

From one side, we employ the idea of factor strength discuss above, trying to use this criteria to select those strong factors.
On the other hand, we use another variable selection method called Elastic Net \cite{Zou2005} to select factors.
With regard of the first approach, \citeA{Bailey2020} provide a consistent estimator for the factor strength, and we will use this method to examine the strength of each candidate factor, and filter out any spurious factors.
Under the second approach, unlike Lasso, elastic net adds an extra penalty term into the loss function, which makes it suitable to handle the potential correlation variables.
This trait makes it suitable for out purpose.
We will assess and compare the methods in their selection of risk factors.
Additionally, we can also use the factor strength as a standard to reduce the dimension of our candidates factor and then applied elastic net to conduct further selection.

%First, we consider the selection of factor base on their strength.
%And then we will use another variable selection method called Elastic Net \cite{Zou2005} to select factors.
%With regard of the first stage, \citeA{Bailey2020} provides a consistent estimates method for the factor strength, and we will use such method to exam the strength of each candidate factors, and filter out those spurious factors, therefore,reduce the dimension of the number of potential factors.
%For the second part, elastic net fixes the problem of Lasso can not handle correlated variables by adding extra penalty term, which makes it suitable for our purpose. 

In the rest of this thesis, we will first go through some literatures relates with CAPM model and methods about factor selection.
Then in the section \ref{strength}, we will provides a detailed description of the concept of factor strength and the estimation method.
Also, we will introduce the elastic net.
In the section \ref{MC}, we set up a simple Monte Carlo simulation experiment to examine the finite sample properties of the factor strength estimator.
Section \ref{Empirical} includes the empirical application, where we estimate the strength of potential risk factors to be included in a CAPM model, as well as apply elastic net as a method to select factors.


%For this project, we are trying to deal with the classical problem: what factors can have significant contributions to explain the asset risk and return relationship under the CAPM framework.
%And we go a step forward, take the correlation among all factors into the account. 
%ut before applying the Elastic Net method, we want to first investigate all those factor's strength.
%Our interest is focused on first determine which factors have enough power to help us solve the risk pricing problem. 
%Then, from this pre-determined relatively small factor group, we applied the Elastic Net method, trying to find out the most appropriate factors to help us form the multi-factor CAPM model.



	\section{Related Literature}
%This project combines three  kinds of literatures: CAPM, factor strength, and factor selection under high dimensioned setting for the number of potential factors.

This project is builds on contributions to the filed of asset pricing.
First formularised by \citeA{Sharpe1964}, \citeA{Lintner1965}, and \citeA{Black1972}, the original CAPM model only contains the market factor, which is denoted by the difference between average market return and risk free return.
\citeA{Fama1992} develop the model into three-factors, which it is then extend into four \cite{Carhart1997}, and five \cite{Fama2015}.
Recent research created a six-factors model and claim it outperform all other sparse factor model. \cite{Kelly2019}.

In terms of assessing the strength of risk factors, this thesis also relates with papers discussing factors that has no or weak correlation with assets' return under the paradigm of CAPM model.
\citeA{Kan1999} found that the test-statistic of FM two-stage regression  \cite{Fama1973} will inflate when incorporating factors which are independent of the cross-section return.
Therefore, when factors with no pricing power was added into the model, those factors may have the chance to pass the significant test falsely.
%\citeA{Kleibergen2009} pointed out how a factor with small loading would deliver a spurious FM two-pass risk premia estimation. 
\citeA{Kleibergen2015} found out that even when some factor-return relationship does not exist, the r-square and the t-statistic of the FM two stage regression would become in favour of the conclusion of such structure presence. 
\citeA{Gospodinov2017} show how the addition of a spurious factor will distort the statistical inference of parameters.
Besides, \citeA{Anatolyev2018} studied the behaviours of the model with the presence of weak factors under asymptotic settings, and they find the regression will lead to an inconsistent risk premia estimation result.
	
	
	Finally, of interest in this thesis is the large dimension of potential factors.
	For this reasons, it borrows from researchers that identify useful factors from a group of potential factors.
\citeA{Harvey2015} examine over 300 factors published in journals, presents that the traditional threshold for a significant test is too low for newly proposed factor, and they suggest to adjust the p-value threshold to around 3. 
Methods like a Bayesian procedure introduced by \citeA{Barillas2018} were used to compare different factor models.
\citeA{Pukthuanthong2019} defined several criteria for "genuine risk factor", and based on those criteria introduced a protocol to examine whether a factor is associated with the risk premium.

%{\bf More details about the previous effort of identifying useful factors }
Once the factor strength are identified, the thesis will attempt to reconcile empirically the factor selection under machine learning techniques and the factor strength implied by the selection.

%This thesis will attempt to address the factor selection problem by using machine learning techniques.
\citeA{Gu2020} elaborate the advantages of using emerging machine learning algorithms in asset pricing.
Those advantages including more accurate prediction result, and superior efficiency.
Various machine learning algorithms have been adopted when selecting factors for the factor model, especially in recent years.
\citeA{Lettau2020} apply Principle Components Analysis when investigating the latent factor of model. 
Lasso method, since it's ability to select features, is popular in the field of the factor selection.
\citeA{Feng2019} used the double-selected Lasso method \cite{Belloni2014},and a grouped lasso method \cite{Huang2010} is used by \citeA{Freyberger2020} when picking factors from a group of candidates. 
\citeA{Kozak2020} used a Bayesian-based method, combing with both Ridge and Lasso regression, arguing that the sparse factor model is ultimately futile. 
